\documentclass[aspectratio=169]{beamer}

\usetheme{metropolis}

\usefonttheme{professionalfonts}
\usepackage[familydefault,light]{Chivo}

\input{common.tex}

\date{\formatdate{20}{10}{2020}}

\institute{supervised by Prof. Dr. Ruth Breu}

\begin{document}
  \maketitle

  \begin{frame}{Outline}
    \begin{itemize}
      \item Motivation
      \item Low-Code Architecture
      \item Model-Driven Architecture
      \item Criticisms
      \item Planned Project Procedure
    \end{itemize}
  \end{frame}

  \begin{frame}{Motivation}
    \begin{itemize}
      \item What can and can't low-code and model-driven tools do?
      \item Are they a viable alternative to traditional development?
      \item When to choose one approach over the other?
    \end{itemize}
  \end{frame}

  \begin{frame}{Low-Code Architecture}
    \begin{itemize}
      \item pre-built application components
      \item graphical user interface for creating application logic as well as
    \end{itemize}
  \end{frame}

  \begin{frame}{Model-Driven Architecture}
    \begin{itemize}
      \item
    \end{itemize}
  \end{frame}

  \begin{frame}{Criticisms}
    \begin{itemize}
      \item Unsuitable for implementing scalable and mission-critical applications.
      \item Do these approaches actually make development easier and cheaper?
      \item Increase in unsupported applications built by shadow IT.
    \end{itemize}
  \end{frame}

  \begin{frame}{Planned Project Procedure}
    \begin{itemize}
      \item evaluate Low-Code tools
      \item evaluate Model-Driven tools
      \item pick two to three of each
      \item compare the two sets with each other
      \item check if a tool fulfils
    \end{itemize}
  \end{frame}
\end{document}
